Architectures and Open pNets

### 2018-10-18 2018-Arch-pNets/arch-pNets.tex
Reading simon;s text : more details on the generation of synch vectors

Intuitively, we 1)~introduce a fresh initial state with an additional
$\init$ transition that initialises all the variables to those defined
by the initial valuation $\val{0}{C}$ of $C$ and 2)~associate an
additional Boolean value to each port, with original transitions of
$C$ marked by $\true$ and additional loop transitions marked by
$\false$.

@@

\paragraph{Encoding the interaction model}
First of all, recall that $\nopri[A, \partition ] \bydef{=}
\pNetTuple{(\nopri[C])^{C \in \cC}, \partition, \nopri[\Gamma]}$.
Thus, the holes in the resulting pNet are indexed by the elements of
partition \partition.  For the encoding of our running example, we
take $\partition = \bigl\{\{\PortFail, \PortResume\},\{\PortAsk,
\PortReset\}\bigr\}$.  This corresponds to the intuition that the
dangling ports {\PortFail} and {\PortResume} correspond to the
monitored events, whereas {\PortAsk} and {\PortReset} correspond to
the actions provided by the ``environment'' (other components of the
system) that are triggered in case of a persistent failure.  Similarly
to the encoding of the corrdinators, in the synchronisation vectors of
\nopri[\Gamma], we will associate Boolean values to the actions
corresponding to these ports.

>>>>

Intuitively, we 1)~introduce a fresh initial state with an additional
$\init$ transition that initialises all the variables to those defined
by the initial valuation $\val{0}{C}$ of $C$ and 2)~define a pNet action algebra that associates, as action parameter, an
additional Boolean value to each port, 3)~create pNet transitions that reflect the original transitions of
$C$ with $\true$ as parameter and 4)~create additional loop transitions marked by
$\false$.

@@

\paragraph{Encoding the interaction model}
First of all, recall that $\nopri[A, \partition ] \bydef{=}
\pNetTuple{(\nopri[C])^{C \in \cC}, \partition, \nopri[\Gamma]}$.
Thus, the holes in the resulting pNet are indexed by the elements of
partition \partition.  For the encoding of our running example, we
take $\partition = \bigl\{\{\PortFail, \PortResume\},\{\PortAsk,
\PortReset\}\bigr\}$.  This corresponds to the intuition that the
dangling ports {\PortFail} and {\PortResume} will be provided by a monitoring component, whereas {\PortAsk} and {\PortReset} correspond to
the actions provided by the ``environment'' (other components of the
system) that are triggered in case of a persistent failure.  Similarly
to the encoding of the coordinators, in the synchronisation vectors of
\nopri[\Gamma], we will associate Boolean values to the actions
corresponding to these ports.
